Automated Topic Naming

### 2012-01-17 ese/ese.tex
Updated exp1-3 discussion on usability/accuracy

Our first word-list set, \textsf{exp1}, was generated using the ontology described in Kayed et al.~\cite{5072519} .
That paper constructs an ontology for software quality measurement using eighty source documents, including research papers and international standards. 
The labels we used:

@@

%\DONE{this discussion is about which DB? where do the numbers come from?}
For \textsf{exp1} the labels with the most topics
were
\emph{correctness} (182/305/748 -- MySQL, MaxDB and PostgreSQL topics) and \emph{testability} (121/238/625). 
We did not see many results for \emph{usability} (4/0/138) or
\emph{accuracy} (3/0/27), which were associated with fewer than ten topics. 
We also looked for correlations between our labels: excluding double
matches (self-correlation), our highest co-occurring terms were
\emph{verifiability} or \emph{correctness}
with \emph{traceability}, and \emph{testability} with \emph{correctness}.% (76 and 62 matches, respectively).
% See the following sections for our error analysis.

@@

For \textsf{exp3}, we generally labelled more topics. 
As we mentioned, the word-lists are broad, so there are likely to be false-positives (discussed below). 
The most frequent label across all projects was \emph{usability}, and the
least frequent label was \emph{maintainability}. 
Common co-occurrences were \emph{reliability} with \emph{usability}, \emph{efficiency} with \emph{reliability}, and \emph{efficiency} with \emph{usability}.
%(200, 190, and 150 topics in common, respectively).

>>>>

Our first word-list set, \textsf{exp1}, was generated using the ontology described in Kayed et al.~\cite{5072519}
That paper constructs an ontology for software quality measurement using eighty source documents, including research papers and international standards. 
The labels we used:

@@

%\DONE{this discussion is about which DB? where do the numbers come from?}
For \textsf{exp1} the labels with the most topics
were
\emph{correctness} (182/305/748 -- MySQL, MaxDB and PostgreSQL topics) and \emph{testability} (121/238/625). 
We did not see many results for \emph{usability} (4/0/138) or
\emph{accuracy} (3/0/27), which were infrequently matched. Note the significantly higher result for \emph{usability} in PostgreSQL -- this suggests a difference in how this project is discussing usability, at least with respect to our analysis.
We also looked for correlations between our labels: excluding double
matches (self-correlation), our highest co-occurring terms were
\emph{verifiability} or \emph{correctness}
with \emph{traceability}, and \emph{testability} with \emph{correctness}.% (76 and 62 matches, respectively).
% See the following sections for our error analysis.

@@

For \textsf{exp3}, we generally labelled more topics. 
As we mentioned, the word-lists are broad, so there are likely to be false-positives (discussed below). 
The most frequent label across all projects (for this wordlist, and unlike \textsf{exp1}) was \emph{usability}, and the
least frequent label was \emph{maintainability}. This implies that our signifiers for usability in this experiment were fairly broad.
Common co-occurrences were \emph{reliability} with \emph{usability}, \emph{efficiency} with \emph{reliability}, and \emph{efficiency} with \emph{usability}.
%(200, 190, and 150 topics in common, respectively).
